### 2019-04-07 papers/journal/problem.tex
Section 5 completed

\subsection{Universal condition}
%Here we will present the QBF.
\noindent We will model the search problem for the universal condition as a quantified Boolean formula (QBF)~\cite{buning2009theory, benedetti2008qbf}, and resultant formula will be solved with the help of a QBF solver.
%
The QBF is a generalization of the Boolean satisfiability problem in which every variable is quantified using either existential or universal quantifiers.
%
The QBFs enables potentially more succinct encodings than SAT but with a higher complexity class decision problem~\cite{buning2009theory}.

>>>>

\subsection{Universal condition}
%Here we will present the QBF.
\noindent We will model the search problem for the universal condition as a quantified Boolean formula (QBF)~\cite{buning2009theory, benedetti2008qbf}, and the resultant formula is solved using a QBF solver.
%
The QBF is a generalization of the Boolean satisfiability problem in which every variable is quantified using either existential or universal quantifier.
%
The QBFs enables potentially more succinct encodings than SAT but with a higher complexity class decision problem~\cite{buning2009theory}.
